### 2017-03-24 thesis/latex/thesis.tex
Thesis: do some shufflin

@@

\begin{document}

\tableofcontents
\listoffigures
\newpage

@@

\subsection{What is dynein?}
\subsubsection{Basics}

Dynein is a cellular structure which converts chemical energy to mechanical energy. It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs). Dynein's mechanical energy is used to transport molecules around the cell, pull chromosomes during division, move cellular propellers known as cilia and various other functions \cite{cianfroccoreview}.\\

@@

Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule. By cycling forward through this ring, the molecule can end up in the same state it began, but moved forward a small amount. This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}. The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data. There are several types of dynein which all behave differently. This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\

\subsubsection{Why do cells need motor transport?}
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2) \textbf{((is this the best way to cite this?))}, a $10^3$ factor difference in size.\\

@@

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}

where D is the diffusion constant describing the diffusability of the biomolecule. For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ %% \cite{diffusionconstants}
, it would take about a month to travel across a millimeter-sized cell. In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

@@

\begin{align}
  X_{nm} &= L_s\left(
  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
  \right)
  \\
  Y_{nm} &= L_s\left(
  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
  \right)
  \\
  X_{t} &= L_n\cos\theta_n\\
  Y_{t} &= L_n\sin\theta_n\\
\end{align}

@@

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
  %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
  %% \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
  %% \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  %% \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
  %% \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}

>>>>

\usepackage{tocbibind}
\usepackage{tocloft}
\usepackage{xpatch}

@@

\begin{document}
\newcommand{\listequationsname}{List of Equations}
\newlistof{myequations}{equ}{\listequationsname}
\newcommand{\myequations}[1]{%
\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}

\xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}

\tableofcontents
\listoffigures
\clearpage
\listofmyequations
\newpage

@@

\subsection{What is dynein?}
\subsubsection{Basics}
Dynein is a cellular structure which converts chemical energy to mechanical energy. It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs). Dynein's mechanical energy is used for various cellular functions, including to transport molecules around the cell, pull chromosomes during division, and move cellular propellers known as cilia \cite{cianfroccoreview}.\\

@@

Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule. By cycling forward through this ring, the molecule will end up in the same state it began, but moved forward a small amount. This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}. The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data. There are several types of dynein which all behave differently. This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\

\subsubsection{Why do cells need motor transport?}
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\

@@

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}
\myequations{some equation}

where D is the diffusion constant describing the diffusability of the biomolecule. For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell. In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same. Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{fig:diffusion_vs_dynein}
\end{figure}

@@

\begin{align}
  X_{nm} &= L_s\left(
  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
  \right)
  \\
  Y_{nm} &= L_s\left(
  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
  \right)
  \\
  X_{t} &= L_n\cos\theta_n\\
  Y_{t} &= L_n\sin\theta_n
\end{align}

@@

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)
  %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
  %% \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
  %% \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  %% \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
  %% \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}
